Figures

### 2016-06-24 figures/figures.rmd
transmission/duration quantile
working on paper

```{r pkgs,warning=FALSE,message=FALSE, echo = FALSE}
library("knitr")
library("ggplot2"); theme_set(theme_bw(base_size = 12,
                                       base_family = "Times"))
opts_chunk$set(echo=FALSE,error=FALSE)
if (.Platform$OS.type=="windows") {
    windowsFonts(Times=windowsFont("Times"))
} 
zero_margin <- theme(panel.margin=grid::unit(0,"lines"))
zero_x_margin <-
    theme(panel.margin.x=grid::unit(0, "lines"))
library("MASS")
## use Dark2 rather than Set1 because colour #6 of Set1 is yellow (ugh/too light)
scale_colour_discrete <- function(...,palette="Dark2") scale_colour_brewer(...,palette=palette)
scale_fill_discrete <- function(...,palette="Dark2") scale_fill_brewer(...,palette=palette)
library("gridExtra")
library("plyr")  ## for ldply()
library("dplyr") ## for full_join()
library("reshape2")  ## for melt()
library("GGally") ## need BMB version
## devtools::install_github("bbolker/GGally")
## devtools::install_github("lionel-/ggstance")
library("ggstance")
```

@@

```{r fig4_func, echo = FALSE}
trim_gg <- function(gg,hack_spaces=TRUE) {
    n <- gg$nrow
    gg$nrow <- gg$ncol <- n-1
    v <- 1:n^2
    gg$plots <- gg$plots[v>n & v%%n!=0]
    gg$xAxisLabels <- gg$xAxisLabels[-n]
    gg$yAxisLabels <- gg$yAxisLabels[-1]
    ## ggpairs tries to parse labels, so this fails if they
    ## have spaces in them ... maybe there's a better way?
    if (hack_spaces) {
        gg$xAxisLabels <- gsub("_"," ",gg$xAxisLabels)
        gg$yAxisLabels <- gsub("_"," ",gg$yAxisLabels)
    }
    return(gg)
}

>>>>

```{r pkgs,warning=FALSE,message=FALSE, echo = FALSE}
library("knitr")
library("ggplot2"); theme_set(theme_bw(base_size = 12,
                                       base_family = "Times"))
library("dplyr")
library("tidyr")
opts_chunk$set(echo=FALSE,error=FALSE)
if (.Platform$OS.type=="windows") {
    windowsFonts(Times=windowsFont("Times"))
} 
zero_margin <- theme(panel.margin=grid::unit(0,"lines"))
zero_x_margin <-
    theme(panel.margin.x=grid::unit(0, "lines"))
library("MASS")
## use Dark2 rather than Set1 because colour #6 of Set1 is yellow (ugh/too light)
scale_colour_discrete <- function(...,palette="Dark2") scale_colour_brewer(...,palette=palette)
scale_fill_discrete <- function(...,palette="Dark2") scale_fill_brewer(...,palette=palette)
library("gridExtra")
library("plyr")  ## for ldply()
library("dplyr") ## for full_join()
library("reshape2")  ## for melt()
library("GGally") ## need BMB version
## devtools::install_github("bbolker/GGally")
## devtools::install_github("lionel-/ggstance")
library("ggstance")
```

@@

```{r sumtab,as.is=TRUE}
rq <- function(x,q,digits=3) {
    round(quantile(x,q),digits)
}
mLtab <- mL.epi %>% group_by(model,variable) %>%
    summarise(lwr=rq(value,0.025),
              med=rq(value,0.5),
              upr=rq(value,0.975)) %>%
    mutate(variable=abbreviate(variable,30)) %>%
    ungroup() %>%
    arrange(variable,model)
kable(mLtab)
```
```{r sumvals,echo=FALSE}
ff <- function(model,variable,r=3) {
    mm <- mLtab[mLtab$model==model & mLtab$variable==variable,3:5]
    round(unlist(mm),r)
}
mindur_random <- ff("random","peak_dur",1)
mindur_pfepc <-  ff("pairform+epc","peak_dur",1)
mindur_implicit  <- ff("implicit","peak_dur",1)
maxt_random <- ff("random","peak_t",2)
maxt_pfepc <- ff("pairform+epc","peak_t",2)
maxt_implicit  <- ff("implicit","peak_t",2)
save(list=ls(pattern="^(maxt|mindur)"),file="../ms/maxminstats.RData")
```
```{r fig4_func, echo = FALSE}
trim_gg <- function(gg,hack_spaces=TRUE) {
    n <- gg$nrow
    gg$nrow <- gg$ncol <- n-1
    v <- 1:n^2
    gg$plots <- gg$plots[v>n & v%%n!=0]
    gg$xAxisLabels <- gg$xAxisLabels[-n]
    gg$yAxisLabels <- gg$yAxisLabels[-1]
    ## ggpairs tries to parse labels, so this fails if they
    ## have spaces in them ... maybe there's a better way?
    if (hack_spaces) {
        gg$xAxisLabels <- gsub("_"," ",gg$xAxisLabels)
        gg$yAxisLabels <- gsub("_"," ",gg$yAxisLabels)
    }
    return(gg)
}
